%-----       letter       ---------------------------------------------------------
% recipient data
\recipient{Company Recruitment team (HR)}{CAPCOM
\\Subject: Graphics Software Engineer}
\date{January 06, 2013}
\opening{Dear Sir or Madam,}
\closing{Yours faithfully,}
\enclosure[Attached]{curriculum vit\ae{}}     % use an optional argument to use a string other than "Enclosure", or redefine \enclname

\makelettertitle

I am PhD student at Telecom ParisTech which is a grand ecole in France.
I am working under the direction of Catherine Pelachaud  and Tamy Boubekeur and will defend my PhD in the end of February 2013. 
I came to know about your job advertisement from Linkedin and  would like to apply for Graphics Software Engineer position in your company. 
Here is a short description of my skills and experience:

I got my master degree in computer science, especially in image processing.
I had half year experience for microscopy image segmentation in Pasteur microscopy.
My major of PhD is 3D rendering and animation and I have significant programming experience as evident in my CV.  
I am familiar with codebases of various sizes and know my way around using shadersystems, trees and real-time animation data. 
Since I have been working on both 3D rendering and animation field, 
I have good knowledge on the graphics pipeline and  succeeded in building an low level animation system for Embodied Virtual Agent system ``Greta'' (new java version, will be released very soon) (http://perso.telecom-paristech.fr/~pelachau/Greta/).

I am proficient in many programming languages especially  C++ and Java. 
I have also designed many interactive real-time 3D applications, all of which involved parallel computations using GLSL, CUDA, etc. 
I have also worked in data mining domain while building human face animation with FACS system.
I would like to request an interview opportunity to show you more details of my project (more information is included in my CV).
Here are my three references:

Catherine Pelachaud (http://perso.telecom-paristech.fr/~pelachau/)
Director of research in CNRS, Professor in Computer Science, Telecom ParisTech (ENST), Paris, France.

Tamy Boubekeur (http://perso.telecom-paristech.fr/~boubek/)
Associate Professor (HDR) in Computer Science, Telecom ParisTech (ENST), Paris, France.

Elmar Eisemann (http://perso.telecom-paristech.fr/~eisemann/)
Professor in Computer Science, TU Delft

\makeletterclosing
