%-----       letter       ---------------------------------------------------------
% recipient data
\recipient{Company Recruitment team (HR)}{Google
\\Subject: Software Engineer - Paris}
\date{January 06, 2013}
\opening{Dear Sir or Madam,}
\closing{Yours faithfully,}
\enclosure[Attached]{curriculum vit\ae{}}     % use an optional argument to use a string other than "Enclosure", or redefine \enclname

\makelettertitle

I will finish my PhD in computer graphics at the end of February 2013. 
Although I am new to the business, I do not lack programming experience and want to put my knowledge into use by developing high-quality computer software and hereby offer my talents to you.

During my studies, I have programmed several coding languages. 
I am especially good at C++ and Java. 
I have been accustomed to use objected oriented programing with design patterns.
I also programmed many interactive real-time 3D applications all of which involved parallel computations using GLSL, CUDA, etc. 
I am familiar with codebases of various sizes and know my way around using shadersystems, trees and real-time animation data. 
Since i have been working both 3D rendering and animation field, I have good acknowledge on the graphics pipeline and i succeed in building an low level animation system for Embodied Virtual Agent system ``Greta''.
Furthermore, i have also investigated in some other algorithms, such as Neural network, some sorting algorithms, etc, which have been implemented in different coding languages in my library.
I hope it can be helpful for my future work.

Studying some specifications (OpenGL, etc) and new algorithms has been a large part of my life in the past years as we were 
always targeting optimizations both speed performance and visual quality.
Some of my work has been presented in different conferences.

I am eager to join the software industry and think that I would be a valuable member of your 
team because I like working with people and my interest in exploiting algorithms is not 
running out of steam. 
I'm looking forward to hearing from you.

\makeletterclosing
